CodeBook
========
This Codebook was generated on `r as.character(Sys.time())`.

Overview
--------

Variable name | Description
--------------|------------
subject       | Subject ID of the 30 volunteers
activity      | Activity name ()
domain        | Time domain signal or frequency domain signal (Time or Freq)
instrument    | Measuring instrument (Accelerometer or Gyroscope)
signal        | Acceleration signal (Body or Gravity)
jerk          | Jerk signal
magnitude     | Magnitude of the signals
axis          | 3-axial signals in the X, Y and Z directions (X, Y, or Z)
measure       | Measure (Mean or SD = standard deviation)
count         | Count of data points
avg           | Average of each variable for each activity and each subject

Dataset structure
-----------------

```{r}
str(data.tidy)
```

Dataset excerpt
---------------

```{r}
data.tidy
```

Summary of variables
--------------------

```{r}
summary(data.tidy)
```

Data preparation
================

1. Download zip-file from https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip 
2. Unzip file
3. Merge the training and test sets to create `one` dataset (`subject_test.txt`,`X_test.txt`,`y_test.txt`,`subject_train.txt`,`X_train.txt`,`y_train.txt`)
4. Name the columns (`features.txt`)
5. Extract only the measurements on the `mean` and `standard deviation` for each measurement
6. Label the target variable with the activity names (`activity_labels.txt`)
7. Reshape data from wide to long format
8. Create new variables for hidden information in the feature description
9. Calculate the average of each variable for each activity and each subject